Spatial Analysis

### 2021-08-05 Scripts/spatial_analisis.Rmd
tweeked function to include extrapolation method

run_tis <- function(input_data, grid, years, taxa, reg){

@@

    partial_df <- bind_rows(
      lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = taxa, reg = regions[r])
    )

@@

  # Set path name
  save_path <- my_path("R","Partial/Interpolation")

@@

# Test me
    # run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Centropristis striata", years = years, reg = regions)

>>>>

run_tis <- function(input_data, grid, years, taxa, reg, method){

@@

    partial_df <- bind_rows(
      lapply(years,tis,input_data = input_data, grid = grid, taxa = taxa, reg = reg[r])
    )

@@

  complement <- paste0("Partial/Interpolation/",method)

  # Set path name
  save_path <- my_path("R",complement)

@@

# Test me
    # run_tis(input_data = ocean_data, grid = grid_eez_fp_df, taxa = "Centropristis striata", years = seq(1970,1980), reg = regions, method = "testa")
